Health Burden (per 100k population) by pathway

### 2023-07-12 results/multi_city/health_impacts/health_pathway_tbls.qmd
Use path specific outcomes instead - ignoring the interactions between AP and PA. Rel #124
Generated results using v30.1 on 120723

---
title: "Health Burden (per 100k population) by pathway"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    page-layout: custom
execute:
  warning: false
  echo: false
---

@@

deaths_pathway <- read_csv(paste0(rel_path, "deaths.csv"))

ylls_pathway <- read_csv(paste0(rel_path, "ylls.csv"))

>>>>

---
title: "Health Burden (per 100k population) by pathway"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    page-layout: custom
    embed-resources: true
execute:
  warning: false
  echo: false
---

@@

deaths_pathway <- read_csv(paste0(rel_path, "deaths_pathway.csv"))

ylls_pathway <- read_csv(paste0(rel_path, "ylls_pathway.csv"))
